Suvut

### 2015-05-10 inst/examples/summary.Rmd
Rmd fixes

```{r, annotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}

@@

missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df3$missing))])
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

@@

```{r, topics, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r, topics2, echo=FALSE, message=FALSE, warning=FALSE}
# Write to file
f <- "output.tables/subjecttopics.tab"
print(paste("Complete subject topic counts in file:", f))
write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
ntop <- 50
```

@@

```{r, topics22, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
```

@@

```{r, authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
a <- rev(rev(sort(table(paste(df$author_family,df$author_first,sep=", "))))[1:ntop])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

@@

```{r, geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geography), ";")))))
```

@@

```{r, geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

```{r, geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

@@

```{r, place, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$city), ";"))))))
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
```

```{r, place2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publicationplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

>>>>

```{r missing, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}

@@

missing <- 100*apply(df, 2, function (x) {mean(is.na(x))})
df2 <- data.frame(list(missing = missing, field = names(missing)))
df2$field <- factor(df2$field, levels = df2$field[rev(order(df2$missing))])
theme_set(theme_bw(15))
p <- ggplot(df2, aes(x = field, y = 100 - missing))
p <- p + geom_bar(stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Documents with data (%)")
print(p)
```

@@

```{r topics1, topics, echo=FALSE, message=FALSE, warning=FALSE}

@@

```{r topics2, echo=FALSE, message=FALSE, warning=FALSE}
# Write to file
f <- "output.tables/subjecttopics.tab"
print(paste("Complete subject topic counts in file:", f))
write.table(cbind(Topic = sort(names(tab))), file = f, sep = "\t", quote = F, row.names = F)
ntop <- 50
```

@@

```{r topics3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mar = c(5, 10, 3, 1)); barplot(rev(rev(sort(table(df$term_topic)))[1:ntop]), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Most common topics")
```

@@

```{r authors, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
a <- rev(rev(sort(table(paste(df$author_family,df$author_first,sep=", "))))[1:ntop])
par(mar = c(5, 10, 3, 1)); barplot(a, horiz = T, las = 1, cex.names = 0.8, xlab = "Documents", main = "Top authors")
```

@@

```{r geo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(unlist(strsplit(as.character(df$term_geography), ";")))))
```

@@

```{r geo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common geographic places")
```

```{r geo3, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/geoplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Geography = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

@@

```{r city, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
tab <- rev(sort(table(str_trim(unlist(strsplit(as.character(df$city), ";"))))))
ntop <- 50
par(mar = c(5, 10, 3, 1)); barplot(log10(rev(tab[1:ntop])), horiz = T, las = 1, cex.names = 0.8, xlab = "Documents (log10)", main = "Most common publication places")
```

```{r city2, echo=FALSE, message=FALSE, warning=FALSE}
f <- "output.tables/publicationplaces.csv"
print(paste("Complete counts in file:", f))
write.table(cbind(Place = names(tab), Documents = tab), file = f, sep = "|", quote = F, row.names = F)
```

### 2015-05-10 inst/examples/suvut.Rmd
Rmd fixes

```{r, annotations, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(family_name))
df2 <- df %>% group_by(family_name) %>% summarise(members = n_distinct(first_name))
df2 <- df2 %>% filter(members > 10) %>% arrange(desc(members))
theme_set(theme_bw(15))
df2$extra <- reorder(df2$family_name, df2$members)
p <- ggplot(df2, aes(x=family_name, y=members))
p <- p + geom_bar(aes(x=extra), data=df2, stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Etunimiä per sukunimi")
print(p)
```

>>>>

```{r suvut, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=15}
df <- readRDS("df.Rdata")
df <- df %>% filter(!is.na(family_name))
df2 <- df %>% group_by(family_name) %>% summarise(members = n_distinct(first_name))
df2 <- df2 %>% filter(members > 10) %>% arrange(desc(members))
theme_set(theme_bw(15))
df2$extra <- reorder(df2$family_name, df2$members)
p <- ggplot(df2, aes(x=family_name, y=members))
p <- p + geom_bar(aes(x=extra), data=df2, stat = "identity")
p <- p + coord_flip()
p <- p + ylab("")
p <- p + xlab("")
p <- p + ggtitle("Etunimiä per sukunimi")
print(p)
```
